\documentclass{article}

% Remember to also load the algostyle.sty file into your project.
\usepackage{algostyle}

% Insert new packages here.

\begin{document}
\begin{question}
You are given a set of $n$ arcs on the unit circle. For a pair of arcs $a_i$ and $a_j$, assume that you can decide if the intersection of $a_i$ and $a_j$ is empty in $O(1)$ time. Describe an $O(n^2)$ algorithm to return the size of the largest set of non-intersecting arcs.

{\bfseries Hint.} {\em Reduce the problem to the straight line version.}
\end{question}

\begin{solution}
Let the anticlockwise direction be the positive direction.
Sort the arcs by the position of their most anticlockwise point, in increasing order,
starting from an arbitrary arc. This takes $O(\log n)$ time.

For each of the $n$ arcs, we can consider it as a starting point in a straight line interval selection problem.
Performing the straight line interval selection problem 
each takes $O(n)$ time since the arcs are already sorted. 
To do this, iterate through the array, starting at a specific arc, adding arcs when they do not intersect with the previous one,
looping back to the beginning of the array of necessary.
This is guaranteed to give the largest set of non-intersecting arcs, given that that specific starting arc was chosen,
as this is just the straight line interval selection problem.
Therefore performing this method for each of the $n$ different possible starting arcs,
will take $O(n^2)$ time.
    
\end{solution}
\end{document}