\documentclass{article}

% Remember to also load the algostyle.sty file into your project.
\usepackage{algostyle}

% Insert new packages here.

\begin{document}
\begin{question}
Let $A[1..n]$ be a sorted array of $n$ {\em distinct} integers. Some of these integers might be positive, negative, or zero.
\begin{enumerate}[label = (\alph*)]
    \item Describe an $O(\log n)$ algorithm to decide if there exist some index $i$ such that $A[i] = i$.

    {\bfseries Hint.} {\em Consider the array $B[i] = A[i] - i$.}

    \item Now, suppose we know that $A[1] > 0$. Describe an $O(1)$ algorithm to decide if there exist some index $i$ such that $A[i] = i$.

    {\bfseries Hint.} {\em Again, consider the array $B[i] = A[i] - i$.}
\end{enumerate}
\end{question}

\begin{rubric}
\begin{itemize}
    \item You should justify why your algorithm is correct and why they run in the allocated time complexities (or faster!).

    \item This task will form part of the portfolio.
    \item Ensure that your argument is clear and keep reworking your solutions until your lab demonstrator is happy with your work.
\end{itemize}
\end{rubric}

\begin{solution}
\begin{enumerate}[label = (\alph*)]
    \item Consider the array $B[i]=A[i]-i$. We want to show that the elements of $B$ are nondecreasing.
    Assume for the sake of contradiction that there exists a $j$ such that $B[j] > B[j + 1]$.
    Substituting the definition of $B$ gives us the inequality $A[j]-j > A[j+1]-(j+1)$, which resolves to 
    $A[j]>A[j+1]-1$. Since the elements are integers, this is equivalent to $A[j]\geq A[j+1]$.
    This is a contradiction, since $A$ is increasing. Therefore $B$ is nondecreasing.

    The proposition that there exists some index $i$ such that $A[i]=i$ is equivalent to the proposition that 
    there exists some index $i$ such that $B[i] = 0$. Performing a binary search on $B$ for the value $0$ will determine if such an index $i$ exists.

    \item Since $A[1]>0$, this means that $B[1]>-1$. As the elements are integers, this implies that $B[1]\geq 0$. 
    In our algorithm, check if $B[1] = 0$. If $B[1] = 0$, then there does exist an index $i$ satisfying the condition.
    Otherwise, $B[1] > 0$. Since $B$ is nondecreasing, it is also the case that all elements in $B$ will be greater than $0$, meaning that no such $i$ exists.

\end{enumerate}
\end{solution}
\end{document}