\documentclass{article}

% Remember to also load the algostyle.sty file into your project.
\usepackage{algostyle}

% Insert new packages here.

\begin{document}
\begin{question}
You are given a set of $n$ intervals $\mathcal I = \{I_1, \dots, I_n\}$ and $n$ colours. Your goal is to assign each interval a colour such that any two intervals that intersect must be assigned different colours. Describe an $O(n \log n)$ algorithm that assigns each interval a colour and uses the minimum number of colours.
\end{question}

\begin{solution}
    The overall idea is to go from left to right, only introducing new colours when 
    there are no others available.
    Represent each interval $I_i$ as a start event $s_i$ and an end event $e_i$.
    The event is just a struct which holds the position, as well as a reference to the interval.
    Sort all events by position from left to right, putting ``end'' events before ``start'' events if they are tied, taking $O(n\log n)$ time.

    Keep a stack of colours that are available to use.
    Perform a sweep from left to right,
    when a start event is encountered, colour its corresponding interval with 
    the top colour on the stack, and pop this colour from the stack.
    If the stack is empty, then we must introduce a new colour and place it on the stack, 
    before popping it from the stack and colouring the interval with this colour.
    When an end event is encountered, find the colour of its corresponding interval, 
    and return this colour onto the stack.
    This sweep takes $O(n)$ time. Thus the complexity of the whole algorithm is $O(n\log n)$ dominated by sorting.

    The number of colours required is at least equal to the maximum number of intervals that are overlapping at once.
    Let this number be $x$.
    This gives a lower bound for the number of colours required.

    Our goal is to show that our greedy algorithm achieves $x$ colours.
    Assume for the sake of contradiction that the greedy algorithm selected a total of $x'$ colours, where $x' > x$.
    The way we defined it, new colours are only introduced when the stack of available colours is empty.
    This means that when the $(x+1)$-th colour was introduced, the stack was empty, meaning that 
    there were $x$ currently-used colours. This means that after the $(x+1)$-th colour is introduced,
    the number of currently-used colours becomes $(x+1)$, meaning that the number of currently intersecting 
    intersections is $(x+1)$. This is a contradiction, since we defined $x$ to be the maximimum number of intersections.

    Therefore this greedy algorithm gives an optimal solution.








\end{solution}
\end{document}