\documentclass{article}

% Remember to also load the algostyle.sty file into your project.
\usepackage{algostyle}

% Insert new packages here.

\begin{document}
\begin{question}
Let $F$ be a flow network with integer capacities. Your task is to return the minimum cut with the smallest number of edges that cross the cut.

\begin{enumerate}[label = (\alph*)]
    \item Consider the new flow network $\hat F$, defined by the new capacity function \[\hat c(x \to y) = c(x \to y) \cdot \left(m + 1\right) + 1,\] where $m$ denotes the number of edges in $F$. Show that if $(S, T)$ is {\em not} a minimum cut of $F$, then $(S, T)$ cannot be a minimum cut of $\hat F$.
    
    {\em This shows that any minimum cut of $\hat F$ must be a minimum cut of $F$.}

    \item Show that the minimum cut of $F$ with the minimum number of edges will have the lowest cut capacity in $\hat F$.

    {\em Hence, the minimum cut of $\hat F$ will be the minimum cut with the smallest number of edges that cross the cut.}
\end{enumerate}
\end{question}

\begin{solution}
\begin{enumerate}[label = (\alph*)]
    \item If $(S,T)$ is not a minimum cut of $F$, then there exists another cut $(S', T')$ such that
    $$c(S',T')<c(S,T).$$
    Let $C$ be the set of edges $(u,v)\in E$ such that $u\in S$ and $v\in T$. 
    In other words, $C$ is the set of edges that cross the cut.
    Similarly, let $C'$ be the set of edges $(u,v)\in E$ such that $u\in S'$ and $v\in T'$.
    By using the definition of cut capacity,
    $$\sum_{(u,v)\in C'} c(u\to v) < \sum_{(u,v)\in C} c(u\to v).$$
    However, since all capacities are integer values, we can strengthen this inequality,
    $$1+\sum_{(u,v)\in C'} c(u\to v) \leq \sum_{(u,v)\in C} c(u\to v).$$
    Multiplying both sides by $(m + 1)$ and then rearranging gives
    \begin{align*}
        (m+1)\left(1+\sum_{(u,v)\in C'} c(u\to v)\right) &\leq (m+1)\sum_{(u,v)\in C} c(u\to v)\\
        m+1+\sum_{(u,v)\in C'} (m+1)\cdot c(u\to v) &\leq \sum_{(u,v)\in C} (m+1)\cdot c(u\to v)
    \end{align*}
    Since $C, C'\subseteq E$, this means $0\leq|C|,|C'|\leq m$. Therefore $|C'|-|C|\leq m$.
    Substituting this into the inequality gives
    \begin{align*}
        |C'|-|C|+1+\sum_{(u,v)\in C'} (m+1)\cdot c(u\to v) &\leq \sum_{(u,v)\in C} (m+1)\cdot c(u\to v)\\
        |C'|+1+\sum_{(u,v)\in C'} (m+1)\cdot c(u\to v) &\leq |C|+\sum_{(u,v)\in C} (m+1)\cdot c(u\to v)\\
        1+\sum_{(u,v)\in C'} ((m+1)\cdot c(u\to v)+1) &\leq \sum_{(u,v)\in C} ((m+1)\cdot c(u\to v)+1)\\
        \sum_{(u,v)\in C'} \hat{c}(u\to v) &<\sum_{(u,v)\in C}\hat{c}(u\to v)\\
        \hat{c}(S',T')&<\hat{c}(S,T).
    \end{align*}
    Therefore $(S',T')$ also has a smaller capacity than $(S,T)$ in $\hat{F}$. Therefore if $(S,T)$ is not a minimum
    cut in $F$, then it is also not a minimum cut in $\hat{F}$.
    
    \item Let $(S,T)$ be a minimum cut on $\hat{F}$. From part (a), $(S,T)$ is also a minimum cut on $F$.
    The capacity $\hat{c}(S,T)$ of a cut $(S,T)$ on $\hat{F}$ can be written as
    \begin{align*}
        \hat{c}(S,T) &= \sum_{(u,v)\in C}\hat{c}(u\to v)\\
        &= \sum_{(u,v)\in C} ((m+1)\cdot c(u\to v)+1)\\
        &= |C| + (m+1)\sum_{(u,v)\in C}c(u\to v)\\
        \hat{c}(S,T) &= |C| + (m+1)\cdot c(S,T)
    \end{align*}

    Since $(S, T)$ is a minimum cut on $F$, the value of $c(S,T)$ is constant no matter what minimum cut we choose.
    Assume for the sake of contradiction that there did exist an alternate cut $(S',T')$ which was minimal on $F$, 
    such that $|C'|<|C|$. Since both cuts are minimal on $F$, their capacities $c(S,T)$ and $c(S',T')$ are equal.
    \begin{align*}
        |C'|&< |C|\\
        |C'|+(m+1)\cdot c(S',T') &< |C|+(m+1)\cdot c(S,T)\\
        \hat{c}(S',T')&< \hat{c}(S,T)
    \end{align*}
    which is a contradiction, since $(S,T)$ was defined to be the minimum cut of $\hat{F}$.

    Therefore $(S,T)$ is the minimum cut on $F$ with the least number of edges crossing the cut.


\end{enumerate}
\end{solution}
\end{document}