\documentclass{article}

% Remember to also load the algostyle.sty file into your project.
\usepackage{algostyle}

% Insert new packages here.

\begin{document}
\begin{question}
Consider the following problem.

\begin{itemize}
    \item[] {\em Let $[n] \coloneqq \{1, \dots, n\}$. What is the size of the largest subset $S \subseteq [n]$ such that every pair of elements in $S$ is coprime?}
\end{itemize}

Let $P_n$ denote the set of primes in $[n]$. It is clear that $S \coloneqq \{1\} \cup P_n$ is a subset that satisfies the condition that every pair of elements in $S$ is coprime. Prove that $\lvert S \rvert$ is correct.

{\bfseries Note.} {\em This implies that the natural greedy algorithm of ``include $x$ iff. $x$ is prime'' returns a subset of maximum cardinality.}

{\bfseries Hint.} {\em There are a few ways to prove this; one way is to define an injection. Another way is to use a standard exchange argument.}
\end{question}

\begin{solution}
    Let $p_i$ be the $i$-th prime number, and let $S_i$ be the set of all positive multiples of $p_i$.
    \begin{align*}
        S_1&=\{2, 4, 6, 8, 10, 12,\dots\}\\
        S_2 &= \{3, 6, 9, 12, 15, 18, \dots\}\\
        S_3 &= \{5, 10, 15, 20, 25, 30, \dots\}
    \end{align*}
    Suppose that $k$ is the largest integer such that $p_k\leq n$.
    Note that all natural numbers greater than $1$ and less than $n$ are contained in the union of $S_1, S_2, \dots, S_k$.
    The coprime subset $S$ can contain at most 1 element from each of 
    $S_1, S_2, \dots, S_k$.
    This is because, if two elements in $S$ were from 
    the same $S_i$, then they would share the common factor $p_i$ which contradicts their coprimality.
    Finally, the set $S$ can also contain the number $1$.
    Thus the upper bound on $|S|$ is $k+1$.

    The set $\{1\}\cup\{p_1, p_2,\dots, p_k\}$ satisfies the condition that every pair of elements in $S$ is coprime.
    Furthermore it has a cardinality of $k+1$. Therefore the size of the largest subset which satsifies the conditions is $k+1$.
    Thus $|S|$ is correct.

\end{solution}
\end{document}